---
title: "Exploratory Data Analysis (EDA) Paper"
author: "Carter Hall, Luis Medrano, Paul Charles, Correy Turral"
date: "June 14, 2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
cbb <- read.csv("../Data/cbb.csv")
```

# Visualize Categorical-Categorical Relation

**Research Question:** Power 5 Conferences are recognized in MBB for their historic prowess; do they appear in the tournament frequently? If so, what seeds do they typically assume?  
**Graph:** 
```{r fig.width=7, fig.height=4}
powerFive <- c("ACC", "SEC", "B10", "B12", "BE")
pfc <- cbb %>% filter(CONF %in% powerFive & !is.na(SEED))
pfc$SEED <- as.factor(pfc$SEED)
ggplot(data = pfc) + geom_histogram(mapping = aes(y = reorder(SEED, desc(SEED))), stat = "count") + 
  facet_wrap(CONF~.) + 
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9,10)) + 
  labs(title = "Appearances in NCAA MBB Tournament for Power 5 Conference By Seed*", 
       subtitle = "From 2013-2019; Four Possible Seeds Per Year", 
       caption = "* - 1-seeds are generally representative of teams more favorited to win the tournament that year. Seeds range from 1-16.", 
       y = "Seed") 
```

**Description (1-sentence):** The Power-5 Conferences have appeared frequently throughout this time period, assuming many of the higher 
seeds the tournament offered.

# Visualize Categorical-Continuous Relation

**Research Question:**  From 2013-2019, which of the Power 5 Conference(s) were the most efficient on offense in the NCAA Tournament?

**Graph:**
```{r}
ggplot(data = pfc, mapping = aes(x = reorder(CONF, ADJOE, FUN = median), y = ADJOE)) + 
  geom_boxplot() + 
  labs(title = "Adjusted Offensive Efficiency of Power 5 Conferences in NCAA MBB Tournament", 
       subtitle = "From 2013-2019 (inclusive)", 
       x = "Conference", 
       caption = "ADJOE: Adjusted Offensive Efficiency: Points Scored per 100 Possessions")
```

**Description (1-sentence):** Based on the result of the boxplot above, we can determine that the ACC was the most efficient conference offensively from 2013 to 2019.

\newpage

# Visualize Continuous-Continuous Relation

**Research Question:** From 2013-2019, is there any relation between win rate and offensive efficiency from all teams in the NCAA Tournament?

**Graph:** 
```{r}
cbb <- cbb %>% mutate(WR = round(W / G, 3))
pfc <- cbb %>% filter(CONF %in% powerFive & !is.na(SEED))
pfc$SEED <- as.factor(pfc$SEED)
ggplot(data = cbb, mapping = aes(x = ADJOE, y = WR)) + geom_point() + 
  geom_smooth(method = lm) + 
  labs(title = "Relationship between Adjusted Offensive Efficiency and Win Rate of MBB Teams in NCAA Tournament", 
       subtitle = "Data shown is of teams in tournaments from 2013-2019.", 
       caption = "WR: Win Rate; ADJOE: Adjusted Offensive Efficiency: Points Scored per 100 Possessions")
```

**Description (1-sentence):** There seems to be a positive strong correlation between offensive efficiency and win rate, with the points of highest win rate showing up at a high offensive efficiency and those with close to zero or zero win rate at a low offensive efficiency.