---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Packages

All of the following packages **should** be used. 

```{r warning = FALSE, message = FALSE}
library(readr)
library(stats)
library(tidyverse)
library(e1071)
library(caTools)
library(class)
```

# Imports

**The origins of these datasets are as follows:**

* - gwd: The 'Cleaning.Rmd' file in the '../Cleaning' directory.
* - cbbAll, cbb20: Kaggle repo that was the original source of data.
* - bpi: 'bpiScraper.Rmd'

```{r}
gwd <- read.csv("../Data/gamesTo2021UPDATED.csv")
allTournYr <- read.csv("../Data/cbbAll.csv")
cbb20 <- read.csv("../Data/cbb20.csv")
bpi <- read.csv("../Data/SOSData.csv")

allTournYr <- allTournYr %>% left_join(bpi, by = c("TEAM", "YEAR"))
cbb20 <- cbb20 %>% left_join(filter(bpi, YEAR == 2020), by = "TEAM") %>% select(-c("YEAR"))

# Lots of Imputing -- Some Teams Did Not Have BPI Records for 1-2 Years
# The imputed values are the mean SOS for the same-seeded teams over the years.
# For teams that did NOT have seeds, I imputed a value well below any other SOS in the dataset.
allTournYr <- allTournYr %>% mutate(SOS = ifelse(is.na(allTournYr$SOS) & allTournYr$SEED == 13, 0.5022333, allTournYr$SOS))
allTournYr <- allTournYr %>% mutate(SOS = ifelse(is.na(allTournYr$SOS) & is.na(allTournYr$SEED), 0.35, allTournYr$SOS))
```

# Analysis Section

## Postseason Berth

### SVM

```{r}
berth <- allTournYr %>% select(c(3:21, 24:26)) %>% mutate(WR = W / G) %>% select(-c(1:2,21))
berth <- cbind(berth[,1:17], berth[,19:20], berth[,18])
colnames(berth)[20] <- c("POSTSEASON")
```

```{r}
set.seed(320)
split = sample.split(berth$POSTSEASON, SplitRatio = 0.80)

train = subset(berth, split == TRUE)
test = subset(berth, split == FALSE)

train_noscale <- train
test_noscale <- test

train[,1:17] <- scale(train[,1:17])
test[,1:17] <- scale(test[,1:17])
```

```{r}
costs=10^(-2:2)
gammas=c(.25,.5,1,2)
ret <- data.frame()

for (cost in costs) {
  for (gamma in gammas) {
    temp_classifier <- svm(formula = POSTSEASON ~ ., data = train, type = 'C-classification', kernel = 'linear', probability = TRUE, cost = cost, gamma = gamma)
    y_pred <- predict(temp_classifier, newdata = test[1:19], probability = TRUE)
    table <- table(test[,20], y_pred)
    acc <- ((table[1,1] + table[2,2]) / (table[1,1] + table[2,2] + table[1,2] + table[2,1]))
    sens <- ((table[1,1]) / (table[1,1] + table[2,1]))
    prec <- ((table[1,1]) / (table[1,1] + table[1,2]))
    
    ret <- rbind(ret, (c(cost, gamma, acc, sens, prec)))
    
  }
}

colnames(ret) <- c("Cost", "Gamma", "Acc", "Sens", "Prec")
```


```{r}
classifier <- svm(formula = POSTSEASON ~ ., data = train, type = 'C-classification', kernel = 'linear', probability = TRUE, cost = 1, gamma = 1)

y_pred <- predict(classifier, newdata = test[1:19], probability = TRUE)
table(test[,20], y_pred)
```

```{r}
test_probs <- attr(y_pred, "probabilities")
test_probs_df <- data.frame(index = rownames(test_probs), prob1 = test_probs[,2], 
          makesPost = ifelse(rownames(test_probs) %in% 
          rownames(test)[which(test$POSTSEASON == 1)], FALSE, TRUE)
          )

test_actuals_df <- data.frame(index = rownames(test), makesPost = test$POSTSEASON)

errors <- test_actuals_df[which(y_pred != test$POSTSEASON),]$index

test_probs_df <- test_probs_df %>% mutate(isError = index %in% errors)

ggplot(data = test_actuals_df, mapping = aes(x = index, y = makesPost)) + 
  geom_point() + 
  geom_point(data = subset(test_probs_df, makesPost == TRUE & isError == FALSE), 
             mapping = aes(x = index, y = prob1), color = "blue") + 
  geom_point(data = subset(test_probs_df, makesPost == TRUE & isError == TRUE), 
             mapping = aes(x = index, y = prob1), color = "blue", size = 3) + 
  geom_point(data = subset(test_probs_df, makesPost == FALSE & isError == FALSE), 
             mapping = aes(x = index, y = prob1), color = "red") + 
  geom_point(data = subset(test_probs_df, makesPost == FALSE & isError == TRUE), 
             mapping = aes(x = index, y = prob1), color = "red", size = 3) +
  scale_y_continuous(breaks = seq(0,1,1), labels = c("False", "True"), 
                     sec.axis = sec_axis(trans~.*1, name = "Probabiltiy of Berth")) + 
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  labs(title = "Predictions for Postseason Births within Testing Data", 
       subtitle = "Original Data of 2013-2021 Games, exc. 2020; See Caption for Color Guide", y = "Received Berth",
       caption = "Blue: Team reached postseason. \n Red: Team did not reach postseason. \n Black: The actual results. \n LARGER SIZES indicate False Positive (Red), False Negative (Blue).", y = "Received Berth") 
```

```{r}
test_noscale <- cbind(test_noscale, y_pred)

ggplot(data = test_noscale, mapping = aes(x = ADJOE, y = ADJDE, color = y_pred)) + geom_point()
ggplot(data = test_noscale, mapping = aes(x = TOR, y = WR, color = y_pred)) + geom_point()
```

## KNN

```{r warning = FALSE}
mean_error <- function(actual, predicted) {
  mean(actual != predicted)
}

ret <- data.frame()

for (k in 1:60) {
  temp_knn <- knn(train, test, cl = factor(train$POSTSEASON), k = k)
  ret <- rbind(ret, c(k, mean_error(test$POSTSEASON, temp_knn)))
}

colnames(ret) <- c("k", "CCE")

plot(ret, type = "b", col = "skyblue", cex = 1, pch = 20, 
     xlab = "k", ylab = "Mean of Classification Error",
     main = "(Test) Error Rate vs Neighbors")
abline(h = mean(ret$CCE), col = "orange", lty = 2)
abline(h = min(ret$CCE), col = "grey", lty = 2)

knn_pb <- knn(train[,1:19], test[,1:19], cl = factor(train$POSTSEASON), k = ret[which(ret$CCE == min(ret$CCE)),1])
```

```{r}
ggplot(data = test_noscale, mapping = aes(x = ADJOE, y = ADJDE, color = knn_pb)) + geom_point()
ggplot(data = test_noscale, mapping = aes(x = TOR, y = WR, color = knn_pb)) + geom_point()
```

## ANN

```{r}
train_x <- train %>% select(-c("POSTSEASON"))
train_y <- train %>% select("POSTSEASON")

test_x <- test %>% select(-c("POSTSEASON"))
test_y <- test %>% select("POSTSEASON")

write.csv(train_x, "../Data/train_x_post.csv", row.names = FALSE)
write.csv(train_y, "../Data/train_y_post.csv", row.names = FALSE)
write.csv(test_x, "../Data/test_x_post.csv", row.names = FALSE)
write.csv(test_y, "../Data/test_y_post.csv", row.names = FALSE)
```

**Now, run the "postseasonNet.py" file found in this directory.**

```{r}
post_model = str_split(read_file("./post_model.txt"), "\r\n")
train_acc_post = as.numeric(post_model[[1]][1])
test_acc_post = as.numeric(post_model[[1]][2])
```

# Seed Prediction

## SVM

```{r}
berth <- allTournYr %>% filter(RESULT != "No Appearance") %>% select(c(3:21, 23,25:26)) %>% mutate(WR = W / G) %>% select(-c(1:2))
berth$SEED <- as.factor(berth$SEED)
```

```{r}
train = berth %>% filter(YEAR <= 2019) %>% select(-c("YEAR"))
test = berth %>% filter(YEAR == 2021) %>% select(-c("YEAR"))
```

```{r}
classifier <- svm(formula = SEED ~ ., data = train, type = 'C-classification', kernel = 'radial', probability = TRUE)

y_pred <- predict(classifier, newdata = test, probability = TRUE)
test_probs <- attr(y_pred, "probabilities")

pred <- c()

for (i in 1:nrow(test_probs)) {
  df <- test_probs[i,]
  pred[i] <- which(df == max(df))
}

results <- cbind(test[,18], pred)
c = 0
for (i in 1:nrow(results)) {
  if (results[i,1] == results[i,2]) {
    c = c + 1
  }
}

```

## KNN

```{r}
mean_error <- function(actual, predicted) {
  mean(actual != predicted)
}

ret <- data.frame()

for (k in 1:60) {
  temp_knn <- knn(train, test, cl = factor(train$SEED), k = k)
  ret <- rbind(ret, c(k, mean_error(test$SEED, temp_knn)))
}

colnames(ret) <- c("k", "CCE")

plot(ret, type = "b", col = "skyblue", cex = 1, pch = 20, 
     xlab = "k", ylab = "Mean of Classification Error",
     main = "(Test) Error Rate vs Neighbors")
abline(h = mean(ret$CCE), col = "orange", lty = 2)
abline(h = min(ret$CCE), col = "grey", lty = 2)

knn_seed <- knn(train[,c(1:17,19:20)], test[,c(1:17,19:20)], cl = factor(train$SEED), k = ret[which(ret$CCE == min(ret$CCE)),1], prob = TRUE)

```

## ANN

```{r}
train_x <- train %>% select(-c("SEED"))
train_y <- train %>% select("SEED")

test_x <- test %>% select(-c("SEED"))
test_y <- test %>% select("SEED")

write.csv(train_x, "../Data/train_x_seeds.csv", row.names = FALSE)
write.csv(train_y, "../Data/train_y_seeds.csv", row.names = FALSE)
write.csv(test_x, "../Data/test_x_seeds.csv", row.names = FALSE)
write.csv(test_y, "../Data/test_y_seeds.csv", row.names = FALSE)
```

```{r}
seed_model = str_split(read_file("./post_model.txt"), "\r\n")
train_acc_seed = as.numeric(seed_model[[1]][1])
test_acc_seed = as.numeric(seed_model[[1]][2])
```

**NOW, run the "seedNet.py" file found in the same directory as this script.**

# Field Generation

## With ANN

```{r}
cbb20 <- read.csv("../data/cbb20Trimmed.csv")
```

```{r}
pred_field <- read.csv("../Data/field2020.csv")
pred_teams <- pred_field %>% select(-c("X", "X0")) %>% rename(prob1 = X1)

pred_teams <- cbind(pred_teams, rank(desc(pred_teams$prob1))) 
colnames(pred_teams)[3] <- "Rank"

pred_teams <- pred_teams %>% filter(Rank <= 68)

fieldData <- cbb20 %>% filter(TEAM %in% pred_teams$TEAM) 
write.csv(fieldData, "../Data/cbb20FINAL.csv", row.names = FALSE)
```

```{r}
seeds_NN <- read.csv("../Data/cbb20SEEDS.csv")
seeds_NN$X0 <- seeds_NN$X0 + 1
seeds_NN <- seeds_NN[,2:3]

seeds_NN <- cbind(seeds_NN, rep(1, nrow(seeds_NN)))
colnames(seeds_NN)[2:3] <- c("Seed", "Berth")
```

## With KNN

```{r}
berth <- allTournYr %>% select(c(3:21, 24:26)) %>% mutate(WR = W / G) %>% select(-c(1:2,21))
berth <- cbind(berth[,1:17], berth[,19:20], berth[,18])
colnames(berth)[20] <- c("POSTSEASON")
```

```{r}
set.seed(320)
split = sample.split(berth$POSTSEASON, SplitRatio = 0.80)

train = subset(berth, split == TRUE)
test = subset(berth, split == FALSE)

train_noscale <- train
test_noscale <- test

train[,1:17] <- scale(train[,1:17])
test[,1:17] <- scale(test[,1:17])
```

```{r}
new_test <- cbb20 %>% mutate(SOS = ifelse(is.na(SOS), mean(na.omit(SOS)), SOS))

ret <- data.frame()

for (k in 1:60) {
  temp_knn <- knn(train[,1:19], scale(new_test[,2:20]), cl = factor(train$POSTSEASON), k = k, prob = TRUE)
  ret <- rbind(ret, c(k, mean_error(test$POSTSEASON, temp_knn)))
}

colnames(ret) <- c("k", "CCE")

knn_pb_2020 <- knn(train[,1:19], scale(new_test[,2:20]), cl = factor(train$POSTSEASON), k = 41, prob = TRUE)

if (table(knn_pb_2020)[2] < 68) {
  needed <- 68 - table(knn_pb_2020)[2]
  knn_not_sure = knn_pb_2020[which(knn_pb_2020 == 0)]
  knn_not_sure_prob = attr(knn_pb_2020, "prob")[which(knn_pb_2020 == 0)]
  indices <- c(which(knn_pb_2020 == 1),
                   which(knn_pb_2020 == 0)[which(order(knn_not_sure_prob) <= needed)])
  
  knn_field_2020 <- new_test[indices,]
} else {
  knn_field_2020 <- new_test[which(knn_pb_2020 == 1)]
}

train <- allTournYr %>% select(c(1:21, 23:26)) %>% mutate(WR = W / G) %>% select(-c(2:4,23:24)) %>% filter(!is.na(SEED))

knn_seed_2020 <- knn(train[,c(2:18,20:21)], knn_field_2020[,2:20], cl = factor(train$SEED), k = 18)

knn_field_2020 <- cbind(knn_field_2020, knn_seed_2020)
colnames(knn_field_2020)[21] <- "Seed"
```

## With SVM

```{r}
berth <- allTournYr %>% select(c(3:21, 24:26)) %>% mutate(WR = W / G) %>% select(-c(1:2,21))
berth <- cbind(berth[,1:17], berth[,19:20], berth[,18])
colnames(berth)[20] <- c("POSTSEASON")
```

```{r}
set.seed(320)
split = sample.split(berth$POSTSEASON, SplitRatio = 0.80)

train = subset(berth, split == TRUE)
test = subset(berth, split == FALSE)

train_noscale <- train
test_noscale <- test

train[,1:17] <- scale(train[,1:17])
test[,1:17] <- scale(test[,1:17])
```

```{r}
classifier <- svm(formula = POSTSEASON ~ ., data = train, type = 'C-classification', kernel = 'linear', probability = TRUE, cost = 1, gamma = 1)

y_pred <- predict(classifier, newdata = new_test[,2:20], probability = TRUE)
```

```{r}
svm_not_sure = which(y_pred == 0)
indices = c(
  svm_not_sure[which(order(attr(y_pred, "probabilities")[svm_not_sure]) <= 22)],
  which(y_pred == 1)
  )

svm_field_2020 <- new_test[indices,]
```

```{r}
train <- allTournYr %>% select(c(1:21, 23:26)) %>% mutate(WR = W / G) %>% select(-c(2:4,23:24)) %>% filter(!is.na(SEED))

classifier <- svm(formula = SEED ~ ., data = train[,2:21], type = 'C-classification', kernel = 'linear', probability = TRUE, cost = 1, gamma = 1)

y_pred <- predict(classifier, newdata = svm_field_2020[,2:20])
svm_seed_2020 <- cbind(svm_field_2020, y_pred)
colnames(svm_seed_2020)[21] <- "Seed"
```

```{r}
total_field <- knn_field_2020 %>% select(c("TEAM", "Seed")) %>% full_join(svm_seed_2020 %>% select(c("TEAM", "Seed")), by = c("TEAM")) %>% full_join(seeds_NN %>% select(c("TEAM", "Seed")), by = c("TEAM"))

automatic <- total_field[complete.cases(total_field),] %>% mutate(Seed.x = as.numeric(Seed.x), Seed.y = as.numeric(Seed.y), Seed = as.numeric(Seed)) %>% rename(KNN = Seed.x, SVM = Seed.y, ANN = Seed) 

means <- c()
for (i in 1:nrow(automatic)) {
  means[i] = (automatic[i,2] + automatic[i,3] + automatic[i,4]) / 3
}

automatic <- automatic %>% cbind(means) %>% arrange(means) %>% cbind(c(1:nrow(automatic))) 
colnames(automatic)[ncol(automatic)] <- "Rank"
automatic <- cbind(automatic, c(rep(1:10, each = 4), 11, 11, 11))
colnames(automatic)[ncol(automatic)] <- "Seed"

at_large <- total_field[-which(automatic$TEAM %in% total_field$TEAM),] 
at_large <- at_large[-which(at_large$TEAM %in% automatic$TEAM),]
at_large <- at_large %>% mutate(Seed.x = as.numeric(Seed.x), Seed.y = as.numeric(Seed.y), Seed = as.numeric(Seed)) %>% rename(KNN = Seed.x, SVM = Seed.y, ANN = Seed)
at_large <- at_large %>% mutate(KNN = ifelse(is.na(KNN), 16, KNN), 
                   SVM = ifelse(is.na(SVM), 16, SVM),
                   ANN = ifelse(is.na(ANN), 16, ANN))
means <- c()
for (i in 1:nrow(at_large)) {
  means[i] = (at_large[i,2] + at_large[i,3] + at_large[i,4]) / 3
}

at_large <- at_large %>% cbind(means) %>% arrange(means) 
at_large <- cbind(at_large, c(1:nrow(at_large))) 
colnames(at_large)[ncol(at_large)] <- "Rank"
at_large <- at_large[1:(68-nrow(automatic)),]
at_large <- cbind(at_large, c(11, 11, 11, rep(12:15, each = 4), rep(16, each = 6)))
colnames(at_large)[ncol(at_large)] <- "Seed"
```

```{r}
predicted_field_final <- rbind(automatic, at_large)
write.csv(predicted_field_final, "../Data/tournamentFINAL.csv", row.names = FALSE)
```

```{r}
tournament <- read.csv("../Data/tournamentFINAL.csv")
cbb20 <- read.csv("../Data/cbb20.csv") %>% select(-c("RK"))
gwd <- read.csv("../Data/gamesTo2021UPDATED.csv") 
```

```{r}
getDifferentials <- function(data) {
  matchup <- data
  ret <- data.frame()
  
  vec <- c()
  names <- c()
  for (i in 5:21) {
    vec[i - 3] <- round(matchup[1,i] - matchup[2,i], 3)
    names[i - 3] <- paste(colnames(matchup)[i], "DIFF", sep = "_")
  }
  names[1] <- "ID"
  vec[1] <- paste(matchup$TEAM[1], matchup$TEAM[2], sep = "-")
  ret <- rbind(ret, vec)
  colnames(ret) <- names
  return(ret)
}
```


```{r}
first_four_11 <- tournament %>% filter(Seed == 11) %>% sample_n(size = 2)
first_four_16 <- tournament %>% filter(Seed == 16) %>% sample_n(size = 2)

first_four_1 <- rbind(first_four_11[1,], first_four_16[1,]) %>% select(-c("KNN":"Rank"))
first_four_2 <- rbind(first_four_11[2,], first_four_16[2,]) %>% select(-c("KNN":"Rank"))
```

```{r}
ff_matchup1 <- rbind(cbb20 %>% filter(TEAM == first_four_1$TEAM[1]),
                     cbb20 %>% filter(TEAM == first_four_1$TEAM[2])) 
ff_matchup2 <- rbind(cbb20 %>% filter(TEAM == first_four_2$TEAM[1]),
                     cbb20 %>% filter(TEAM == first_four_2$TEAM[2]))

ff_matchup1_diff <- getDifferentials(ff_matchup1)
ff_matchup2_diff <- getDifferentials(ff_matchup2)

round_of_64 <- tournament[-c(which(tournament$TEAM %in% first_four_11$TEAM | 
                      tournament$TEAM %in% first_four_16$TEAM)),]

makeRegions <- function(data, i) {
  ret <- data.frame()
  for (j in 1:16) {
    ret <- rbind(ret, 
                 cbb20 %>% filter(TEAM == (data %>% filter(Seed == j))$TEAM[i]))
  }
  return(ret)
}

east <- makeRegions(round_of_64, 1)
south <- makeRegions(round_of_64, 2)
midwest <- makeRegions(round_of_64, 3)
west <- makeRegions(round_of_64, 4)
```

```{r}
makeMatchups <- function(region) {
  ret <- data.frame()
  for (i in 0:((nrow(region)/2) - 1)) {
    ret <- rbind(ret, getDifferentials(rbind(region[i + 1,], region[nrow(region)-i,])))
  }
  
  ret[,2:ncol(ret)] <- ret[,2:ncol(ret)] %>% mutate_if(is.character, as.numeric)
  
  return(ret)
}

east_R64 <- makeMatchups(east)
south_R64 <- makeMatchups(south)
midwest_R64 <- makeMatchups(midwest)
west_R64 <- makeMatchups(west)
```

```{r}
diffs <- gwd[,c(8,11:27)]

scoreDiffMod <- glm(formula = ScoreDiff ~ ADJOE_DIFF + ADJDE_DIFF + TORD_DIFF + 
    WAB_DIFF, data = diffs)

simulate <- function(games, name) {
  diffs <- predict.lm(scoreDiffMod, games)
  splits <- strsplit(games$ID, split = "-")
  teams <- c()
  
  for (i in 1:length(splits)) {
    if (diffs[i] > 0) {
      teams[i] <- splits[[i]][1]
    }
    else {
      teams[i] <- splits[[i]][2]
    }
  }
  
  ret <- data.frame(cbind(games$ID, round(diffs, 1), teams, rep(name, each = i)))
  colnames(ret) <- c("ID", "DIFF", "TEAM")
  return(ret)
}

updateRegions <- function(data) {
  ret <- data.frame()
  for (i in 1:nrow(data)) {
    ret <- rbind(ret, cbb20 %>% filter(TEAM == data$TEAM[i]))
  }
  return(ret)
}
ff_matchup1_diff[,2:ncol(ff_matchup1_diff)] <- ff_matchup1_diff[,2:ncol(ff_matchup1_diff)] %>% mutate_if(is.character, as.numeric)
ff_matchup2_diff[,2:ncol(ff_matchup2_diff)] <- ff_matchup2_diff[,2:ncol(ff_matchup2_diff)] %>% mutate_if(is.character, as.numeric)

first_four1 <- simulate(ff_matchup1_diff, "First Four")
first_four2 <- simulate(ff_matchup2_diff, "First Four")

east_Round1 <- simulate(east_R64, "East - Round of 64")
east_Round2 <- simulate(makeMatchups(updateRegions(east_Round1)), "East - Round of 32")
east_Round3 <- simulate(makeMatchups(updateRegions(east_Round2)), "East - Sweet 16")
east_final <- simulate(makeMatchups(updateRegions(east_Round3)), "East - Elite 8")

west_Round1 <- simulate(west_R64, "West - Round of 64")
west_Round2 <- simulate(makeMatchups(updateRegions(west_Round1)), "West - Round of 32")
west_Round3 <- simulate(makeMatchups(updateRegions(west_Round2)), "West - Sweet 16")
west_final <- simulate(makeMatchups(updateRegions(west_Round3)), "West - Elite 8")

midwest_Round1 <- simulate(midwest_R64, "Midwest - Round of 64")
midwest_Round2 <- simulate(makeMatchups(updateRegions(midwest_Round1)), "Midwest - Round of 32")
midwest_Round3 <- simulate(makeMatchups(updateRegions(midwest_Round2)), "Midwest - Sweet 16")
midwest_final <- simulate(makeMatchups(updateRegions(midwest_Round3)), "Midwest - Elite 8")

south_Round1 <- simulate(south_R64, "South - Round of 64")
south_Round2 <- simulate(makeMatchups(updateRegions(south_Round1)), "South - Round of 32")
south_Round3 <- simulate(makeMatchups(updateRegions(south_Round2)), "South - Sweet 16")
south_final <- simulate(makeMatchups(updateRegions(south_Round3)), "South - Elite 8")

final_four1 <- simulate(makeMatchups(updateRegions(rbind(east_final, west_final))),
                        "Final Four (East vs. West)")
final_four2 <- simulate(makeMatchups(updateRegions(rbind(south_final, midwest_final))),
                        "Final Four (South vs. Midwest)")

championship <- simulate(makeMatchups(updateRegions(rbind(final_four1, final_four2))),
                         "Championship Game")
```

```{r}
tourney <- rbind(
  first_four1,
  first_four2,
  east_Round1,
  east_Round2,
  east_Round3,
  east_final,
  west_Round1,
  west_Round2,
  west_Round3,
  west_final,
  midwest_Round1,
  midwest_Round2,
  midwest_Round3,
  midwest_final,
  south_Round1,
  south_Round2,
  south_Round3,
  south_final,
  final_four1,
  final_four2,
  championship
)

write.csv(tourney, "../Data/tourneySimulated.csv", row.names = FALSE)
```

# Presentation: EDA Section

```{r}
gwd <- read.csv("../Data/gamesTo2021UPDATED.csv")
allTournYr <- read.csv("../Data/cbbAll.csv")
cbb20 <- read.csv("../Data/cbb20.csv")
bpi <- read.csv("../Data/SOSData.csv")

allTournYr <- allTournYr %>% left_join(bpi, by = c("TEAM", "YEAR"))
cbb20 <- cbb20 %>% left_join(filter(bpi, YEAR == 2020), by = "TEAM") %>% select(-c("YEAR"))

# Lots of Imputing -- Some Teams Did Not Have BPI Records for 1-2 Years
# The imputed values are the mean SOS for the same-seeded teams over the years.
# For teams that did NOT have seeds, I imputed a value well below any other SOS in the dataset.
allTournYr <- allTournYr %>% mutate(SOS = ifelse(is.na(allTournYr$SOS) & allTournYr$SEED == 13, 0.5022333, allTournYr$SOS))
allTournYr <- allTournYr %>% mutate(SOS = ifelse(is.na(allTournYr$SOS) & is.na(allTournYr$SEED), 0.35, allTournYr$SOS))

berth <- allTournYr %>% select(c(3:21, 24:26)) %>% mutate(WR = W / G) %>% select(-c(1:2,21))
berth <- cbind(berth[,1:17], berth[,19:20], berth[,18])
colnames(berth)[20] <- c("POSTSEASON")
```

```{r}
library(GGally)

vars = c("ADJOE", "ADJDE", "ORB", "TOR", "WR")
data1 <- berth[,c(vars)]
drop_na(data1)
ggpairs(data1, progress = FALSE, 
        upper = list(continuous = "cor"),
        lower = list(continuous = "density")
        )
ggsave("../Data/Images/corr_dens_plot.png")
```
